### 2023-01-11 paper-thesis/chapters/02-background-spoofax.tex
Work on section 3
x

@@

\section{\label{sec:statix} Statix and Scope graphs}

@@

% CREDIT FOR THIS EXPLANATION TO ARON ZWAAN
% HOW TO CREDIT?

>>>>

This chapter will explain the concepts behind the Spoofax Language Workbench. If you are already familiar with Spoofax, you can skip this chapter.

\section{Spoofax}

@@

\section{\label{sec:statix}Statix and Scope graphs}

\textit{Note: This section is adapted from the Explanation in "Composable Type System Specification
	using Heterogeneous Scope Graphs". \cite[sect. 4.1.2]{Zwaan21}}

@@
